\section{Assignment Description}
The assignment we received was to create an imaging application which read the metadata of an image, and stored it in a database. 
The user had to be able to register images, and when images are added, their metadata is read and added to the database. The user also had to be able to search based on metadata and on the tags added by the user. Lastly the user had to have the possibility to create a PDF photo album.
The goal was to develop this application from scratch.

The client which has given the assignment is Evil inc. They needed an imaging application which reads the metadata of images. 

The technical requirements the application had to fulfill is as follows:
\begin{itemize}
    \item Must be a standalone Java application.
    \item Use the MySQL database at the university and use ORM technology.
    \item Use a connection pool with one connection.
    \item Test at least all the classes that read image metadata with JUnit.
    \item Has to follow the Web Content Accessibility Guidelines.
\end{itemize}

The project also had some process requirements:
The project had to be carried out in three iterations.
\begin{enumerate}
    \item The 1st iteration focused on the vision and the requirements. A wireframe of the application had to be made and usability testing had to be done. The prototype and the vision document had to be provided in the 1st iteration.
    \item In the 2nd iteration the focus was placed on the MVP. This was a prototype with minimal functionality. This prototype was also usability tested. The first version of the GitLab WIKI was also made.
    \item In the 3rd iteration the focus was on finishing the application and all documents. 
\end{enumerate}
