\section{Introduction}

\subsection{The purpose of the report}
The purpose is to give the reader information about the development process of the application. The intent is for the reader to understand how the project was solved. This includes the whole project from start to finish, including the requirements and thought process behind the decisions that were made during development.

\subsection{Scope}
This report contains the information about the development process for the application MetIma. The name MetIma is a combination of the words \textit{metadata} and \textit{image}. The application is primarily an imaging application which reads the metadata of images and saves it in a accessible database. This report covers all the different elements from the process, as well as how the process was structured.

As for the application itself, and its position in the market, MetIma is part of a very competitive space. With already well established similar applications like Picasa and Photoscape, MetIma will have a hard time acquiring users that already use these applications. At the same time, one of MetImas differentiating features is that it is very lightweight and tailored towards users that prefer a simple to use interface. This could entice users to switch over to MetIma if it offers all the functionality they need in a software like it. MetIma also has the advantage of being commissioned by a customer, so it has a guaranteed user base.

\newpage

\subsection{Definitions, Acronyms and Abbreviations}
In the report, there are a lot of terms used that might not have an obvious meaning by themselves. Therefore, a list of these terms and their explanations have been included:
\begin{itemize}
    \item IDE - \textbf{I}ntegrated \textbf{d}evelopment \textbf{e}nvironment.
    \item NTNU - Norwegian University of Science and Technology. (\textbf{N}orges \textbf{t}eknisk-\textbf{n}aturvitenskapelige \textbf{u}niversitet)
    \item WCAG - \textbf{W}eb \textbf{C}ontent \textbf{A}ccessibility \textbf{G}uidelines 
    \item MVP - \textbf{M}inimum \textbf{v}iable \textbf{p}roduct
    \item GUI - \textbf{G}raphical \textbf{u}ser
    \textbf{i}nterface
    \item VoIP - \textbf{V}oice over \textbf{I}nternet \textbf{P}rotocol
    \item DevOps - Software development (Dev) and Information-technology operations (Ops)
    \item ORM - \textbf{O}bject-\textbf{r}elational \textbf{m}apping
\end{itemize}


\subsection{Overview}
This report explains what the project is and how it was solved. There is also additional information regarding the application, and its functions. The report goes into detail about how the development team collaborated and solved problems during the project. 


